The force-free magnetosphere of a Kerr black hole: the role of boundary conditions

### 2018-06-20 paper/ms.tex
state save

The boundary conditions on the polar axis, on the horizon and at infinity are natural.

\begin{subequations}
\begin{align}
    A_\phi(\mu = 1) &= 0,  \label{eq:bc1}\\
    \Am(\mu = 0, r > 2) &= 0, \label{eq:bc2}\\
    B^2-E^2 (\mu = 0, r_+ \leq r \leq 2) &=0.\label{eq:bc3}
\end{align}
\end{subequations}
where $r_+$ is the radius of the event horizon.

@@

\subsection{Numerical method}
We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ satisfying the radiation condition
\be I = 2\Omega A_\phi, \label{eq:rad}\ee
and enabling field lines smoothly crossing the LS,
and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
guaranteeing the boundary condition (\ref{eq:bc3}).

In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
and implement a uniform $512\times 64$ grid. The detailed algorithm is listed as follows.

1. We choose an initial guess for the field configuration, $\Omega(\Ap)$, $I(\Ap)$
and equator boundary condition as follows
\begin{subequations}
\begin{align}
    \Ap &= r^2 \sst,  \label{eq:gss1} \\
    \Omega & = 0.5\WH\left(1-\Ap/\AHE\right),  \label{eq:gss2}\\
    I & = \WH \Ap\left(1-\Ap/\AHE\right) , \\
    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3, \label{eq:gss3}
\end{align}
\end{subequations}
where $\WH = a/2r_+$ is the BH angular velocity.

@@

In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
which displays two generic features: 1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
2) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
both of which carry electric current and therefore Poynting flux.

@@

>>>>

The boundary conditions
\begin{subequations}
\begin{align}
    A_\phi(\mu = 1) &= 0,  \label{eq:bc1}\\
    \Am(\mu = 0, r > 2) &= 0, \label{eq:bc2}\\
    B^2-E^2 (\mu = 0, r_+ \leq r \leq 2) &=0.\label{eq:bc3}
\end{align}
\end{subequations}
where $r_+$ is the radius of the event horizon.

@@

\subsection{Numerical method}
We aim to find a pair of $\Omega(A_\phi)$ and $I(A_\phi)$ connected by the radiation condition
\be I = 2\Omega A_\phi, \label{eq:rad}\ee
and enabling field lines smoothly crossing the LS,
and suitable normal derivative $\Am(\mu =0, r_+\leq r \leq 2)$ on the equator
guaranteeing the boundary condition (\ref{eq:bc3}).

In our computation, we define a new radial coordinate $R=r/(1+r)$, confine our
computation domain $R\times \mu$ in the region $[R(r_+), 1]\times [0,1]$,
and implement a uniform $512\times 64$ grid. The detailed algorithm is clarified
in the following steps.

1. We choose an initial guess for the field configuration, functions
$\{ \Omega(\Ap), I(\Ap)\}$
and equatorial boundary condition as follows
\begin{subequations}
\begin{align}
    \Ap &= r^2 \sst,  \label{eq:gss1} \\
    \Omega & = 0.5\WH\left(1-\Ap/\AHE\right),  \label{eq:gss2}\\
    I & = \WH \Ap\left(1-\Ap/\AHE\right) , \\
    \Am(\mu =0, r_+\leq r \leq 2) & = - (r/r_+)^3, \label{eq:gss3}
\end{align}
\end{subequations}
where $\WH = a/2r_+$ is the angular velocity of the BH.

@@

In Figure \ref{fig:field_lines}, we plot the magnetic field lines enclosing a BH with spin $a =0.99$ as an example,
which displays three generic features: (1) the LS runs from $r=r_+$ to $r=2M$ as $\theta$ varies from $0$ to $\pi/2$,
(2) there is no current sheet within the magnetosphere except the equatorial current sheet extending from $r_+$ to $2M$,
which gives rise to a cusp to the magnetic field lines,
(3) magnetic field lines entering the ergosphere end up either on the horizon or on the equatorial current sheet,
both of which carry electric current and therefore Poynting flux.

@@

\subsection{Solution uniqueness}

\subsection{Topology of near-horizon field lines}
